---
title: 'Developing Data Products: Week 3 Assignment'
author: "Krishna"
date: "7/22/2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

##<b>Instructions</b></br>
Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. 

Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity!

##<b>Notice</b></br>
To run the presentation in R install:</br>

  [1] Plotly with the command: install.packages("plotly")</br>
  [2] Load the library with: library(plotly)</br>
  [3] Load the library with: library(gapminder)
  
##<b>Project Summary</b></br>
This assignment is to display some information using plotly presentation.
  
```{r echo=FALSE, warning=FALSE, message=FALSE }
library(ggplot2)
library(plotly)
library(gapminder)
```
## Gapminder Bubble Plot (2007)

```{r echo=FALSE, warning=FALSE, message=FALSE}

gDat <- gapminder
jDat <- droplevels(subset(gDat, continent != "Oceania"))

colorsURL <- "http://www.stat.ubc.ca/~jenny/notOcto/STAT545A/examples/gapminder/data/gapminderCountryColors.txt"
countryColors <- read.delim(file = colorsURL, header=TRUE, as.is = 3) 

#countryColors <- read.delim(file="CountryColors", header=TRUE, as.is = 3)

jColors <- countryColors$color
names(jColors) <- countryColors$country

jYear <- 2007

jDat <- jDat[with(jDat, order(year, -1 * pop)), ]
gap.bubble.plot <- ggplot(subset(jDat, year == jYear),
       aes(x = gdpPercap, y = lifeExp )) + scale_x_log10() +
  geom_point(aes(size = sqrt(pop/pi), text = paste(country, lifeExp, "years")), pch = 21) + 
  scale_size_continuous(range=c(1,40)) +
  facet_wrap(~ continent) + 
  aes(fill = country) + scale_fill_manual(values = jColors) + theme(legend.position="none") +
  xlab("GDP Per Capita\n") + ylab("\nLife Expectancy")


ggplotly(gap.bubble.plot, tooltip=c("text"))

```
